Reply to reviewers concerning submission sensors-238686: "An efficient audio coding scheme for quantitative and qualitative large scale acoustic monitoring using the sensor grid approach"

### 2017-11-15 paper/sensors/coverLetter.tex
cover letter proof read

$\rightarrow$ While a single audio channel was selected for this study, a multiple channel encoding can be performed by applying the Delta compression along both the time and channels dimensions. As the transmitted data primarily consists of energetic measurements, additional channels are likely to be encoded very efficiently due to the redundance of information already contained in the first channel.

@@

$\rightarrow$ Following this comment as well as the comment of Reviewer III, we reworked the introduction to match this format. The considerations on acoustic monitoring and event detection in urban sound environments previously discussed in Section 2 have also been moved earlier in the introduction. A new section (Section 2.1) was added to discuss the choice of data representation.

@@

$\rightarrow$ The main contribution of this work, which is now more clearly shown in the introduction, is about the definition of a coding scheme that will be used (as stated in the conclusion) in a sensor network. But prior to this usage, several properties needed to be validated, motivating this work.

@@

$\rightarrow$ We added more references bewteen sections to facilitate the reader's orientation in the manuscript.

@@

$\rightarrow$ As is now explained in Section 3.2, we do not aim at achieving the best classification performance but 1) to prove that third-octave bands match the most commonly used descriptors for the classification task, and 2) to discuss the effect of encoding parameters on the recognition accuracy to select the most appropriate. To this aim we chose to replicate the baseline results for the considered dataset on these four schemes.
The study of more advanced classification schemes and of deep learning for AED will however be of particular interest in future related work.

@@

@@

$\rightarrow$ As stated in the introduction and conclusion, the proposed scheme will be applied to a sensor grid as part of the CENSE project. However, as this sensor grid is not yet implemented, the UrbanSound8k dataset provides both a decent amount of audio data with similar content (urban environmental sounds) and classification methods and results that can be used as a baseline for our work.

@@

$\rightarrow$ The contribution of this work is on the coding only. To the best of our knowledge the proposed approach is the only scheme where the data transmitted is not the detected events nor the raw audio but an intermediate spectral based format, specifically designed for acoustic monitoring and AED.

@@

$\rightarrow$ While we are aware that standardized metrics exist such as the ITU protocols, we believe that they are not adapted to the evaluation of intelligibility in this application. The encoding process distorts the signal in a very non-linear way, so that we have no control over the background and signal elements. A five-point score on the overall intelligibility is however used, and a second metric (the transcription ratio) is designed to account for the typical distortions induced by linearly scaled spectrogram and phase recoveries. Motivation and insight concerning the used metrics are now added in Section 3.3.

>>>>

$\rightarrow$ While a single audio channel was selected for this study, a multiple channel encoding can be performed by applying the Delta compression along both the time and channels dimensions. As the transmitted data primarily consists of energetic measurements, additional channels are likely to be encoded very efficiently due to the redundancy of information already contained in the first channel.

FELIX : reference to where the article has been modified.

@@

$\rightarrow$ Following your comment as well as the comment of Reviewer III, we have rewritten the introduction to better highlight the contributions of the paper. The considerations on acoustic monitoring and event detection in urban sound environments previously discussed in Section 2 have also been moved earlier in the introduction to better frame those contributions. A new section (Section 2.1) was added to discuss the choice of data representation.

@@

$\rightarrow$ The main contribution of this work, which is now more clearly shown in the introduction, is about the definition of a coding scheme that will be used (as stated in the conclusion) in a sensor network that will be implemented in a near future. But prior to this usage, several properties needed to be validated, motivating this work.

@@

$\rightarrow$ We added more references between sections to facilitate the reader's orientation in the manuscript.

@@

$\rightarrow$ As is now explained in Section 3.2, we do not aim at achieving the best classification performance but 1) to prove that third-octave bands match the most commonly used descriptors for the classification task, and 2) to discuss the effect of encoding parameters on the recognition accuracy to select the most appropriate. To this aim we chose to replicate the baseline results for the considered dataset on these four schemes.
The study of more advanced classification schemes and of deep learning for AED is very interesting and will be of particular interest in future work.

@@

FELIX give ref to where you discuss this the paper.

@@

$\rightarrow$ As now more clearly stated in the introduction and conclusion, the proposed scheme will be applied to a sensor grid as part of the CENSE project. However, as this sensor grid is not yet implemented, the UrbanSound8k dataset provides both a decent amount of audio data with similar content (urban environmental sounds) and classification methods and results that can be used as a baseline for our work.

@@

$\rightarrow$ The contribution of this work is on the coding only. As discussed in the introduction, to the best of our knowledge the proposed approach is the only scheme where the data transmitted is not the detected events nor the raw audio but an intermediate spectral based format, specifically designed for acoustic monitoring and AED, thus motivating this paper.

@@

$\rightarrow$ While we are aware that standardized metrics exist such as the ITU protocols, we found that they are not adapted to the evaluation of intelligibility in this application. The encoding process distorts the signal in a very non-linear way, so that we have no control over the background and signal elements. A five-point score on the overall intelligibility is still used however, and a second metric (the transcription ratio) is designed to account for the typical distortions induced by linearly scaled spectrogram and phase recoveries. Motivation and insights concerning the used metrics as well as this discussion are now added in Section 3.3.
